Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/introduction.tex
Added URL for SystemOnTPTP.

Proof-reconstruction address this problem. It becomes in mostly cases
a reverse engineering task to verify the prover reasoning. That
usually happen when the reconstruction is made by another and not by
the developers of the \ATP. The presentation of the proofs generated
by the prover play an important role in proof-reconstruction. To
verify such a proof, it is convenient to have it in a consistent
format, that is, a full script describing step-by-step with exhaustive
details and without ambiguities, the derivation to get the proof. For
classical propositional logic (henceforth \CPL) from a list of at
least forty \ATPs---available from the Web service \name{SystemOnTPTP}
of the TPTP World---just few of them show their proofs.

>>>>

Proof-reconstruction address this problem. It becomes in mostly cases
a reverse engineering task to verify the prover reasoning. That
usually happen when the reconstruction is made by another and not by
the developers of the \ATP. The presentation of the proofs generated
by the prover play an important role in proof-reconstruction. To
verify such a proof, it is convenient to have it in a consistent
format, that is, a full script describing step-by-step with exhaustive
details and without ambiguities, the derivation to get the proof. For
classical propositional logic (henceforth \CPL) from a list of at
least forty \ATPs---available from the Web service \name{SystemOnTPTP}
of the TPTP
World\footnote{\url{http://www.cs.miami.edu/~tptp/}.}---just few of
them show their proofs.
